Title

### 2023-09-20 main.tex
Cambios menores

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels. \revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo}
 Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity.  \\

@@

Here, our systems always consist of some number $N$ of qubits.
The qubits can be divided into the ones to which we will apply the quantum channel, or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
The circuit implements a unitary operator $U$ and then some or all of the qubits are measured.
}

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
\tbnote{La respuesta a esto puede incluir lo siguiente: 
It works better for depolarizing channels, yes, but still has considerably big zone with high fidelity.}
 This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels \revnote{why?} (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{As I see it, an advantage is that only one circuit arrengment is needed for any channel. We don't have to change
the circuit to implement different channels, only need to change parameters.
This allows us to consider parametrized circuits and then explore what happens when
we constrain to only one parametrized operation.}

{\color{green}
\subsection{Two-qubit Pauli channels}
\tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}

For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two principal
qubits and $2N$ ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the number of ancilla qubits can be reduced for Pauli 
channels in which not all two-qubit Pauli matrices are applied to
the system. For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  (\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  (\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}a).

@@

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer and we obtained the Choi 
matrix by doing quantum process tomography on
the two principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}b).

@@

{\color{green} As before, from the definition of a 1PR, we know that $U(p)$ can be decomposed as $ARB$, where 
$A,B$ are unitary operators acting on the $N$-qubit system
and $R$ is a rotation applied to one qubit.
From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$ rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones. 
To prove the result, we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
then $R_{\sigma_3}(2s(p))$ and finally $A$, with
the goal of getting to \eref{eq:uj}. }

@@

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{Fig4}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. There is some freedom when defining
the operators $A$ and $B$, we only need
to make sure that: \revnote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?} 
\tbnote{Reescribí la oración anterior para no decir que es una definición,
sino que queda algo de libertad (aunque igual lo decía después de la ecuación}
\begin{align}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \nonumber \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\label{eq:BA}
\end{align}
\revnote{Please, at least give an example of this semiarbitrary construction of A and B.}
\tbnote{Hay ejemplos en los ejemplos de abajo.}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary. 
Then, by following the calculations of applying 
$A R_{\sigma_3}(2s(p)) B$ to $|0\rangle$,
it can be shown that the curve of states created is that described in \eref{eq:curve-states}.
\revnote{I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
\tbnote{Reescrib\'i la oraci\'on anterior de forma que creo que se entiende mejor.}

To see that $A R_{\sigma_3}(s(p)) B |0\rangle$ in fact creates
the curve of states described in \eref{eq:curve-states}, \revnote{to see what?} \tbnote{Ya cambié la oración anterior} we can rewrite the expression of $B|0\rangle$ by 
separating the first $N-1$ qubits from the last one:
$$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
Since the parametrized rotation $R_{\sigma_3}(2s(p))$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain: \revnote{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \tbnote{No entiendo la pregunta, pero creo que la respuesta es no}

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that ${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 =
{|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.  Then, taking the $\beta_j$ to be
real, the curve of states can be 
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle 
      - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle 
      + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right) \\
\equiv & e^{is} |a\rangle + e^{-is} |b\rangle
\end{align*}
\revnote{to be consistent with the previous formalism, the states should be 0,1,2,3} \tbnote{Done.}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
Explicitly, following the discussion after theorem \ref{theorem2},
we know that this curve of states can be constructed by 
the circuit of \fref{FigS2q}.

@@

Now, defining $A$ and $B$ as in  \eref{eq:BA} for the particular
vectors $|a\rangle, |b\rangle, |c \rangle$ of this dynamical map, we have that
\begin{align*}
A = \begin{pmatrix}
0 & 0 & 1/\sqrt{2} & 1/\sqrt{2} \\
1/\sqrt{6} & -1/\sqrt{2} & i /\sqrt{6} & -i /\sqrt{6} \\
1/\sqrt{6}  & 1/\sqrt{2} & i/\sqrt{6} & -i/\sqrt{6} \\
-\sqrt{2/3} & 0 & i/\sqrt{6} & -i/\sqrt{6}
\end{pmatrix} \; , \; B = \begin{pmatrix}
0 & 0 & 0& 1 \\
0 & 0 & 1 & 0 \\
1/\sqrt{2} & -1/\sqrt{2} & 0 & 0 \\
1/\sqrt{2} & 1/\sqrt{2} & 0 & 0 
\end{pmatrix}
\end{align*}
where the first column of $A$ and the
last three of $B$ can be chosen arbitrarily as long as the resultant matrices are unitary. 
We ran this circuit in IBM's quantum computer ibmq-lima for $25$ different values of $p$ between $0$ and $1$,
and $20$ repetitions for each value of $p$.
The diamond fidelity was calculated in each case and is shown in \fref{fid}.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) =  {(1-p)}^2  \rho + (p-p^2) \sigma_1 \rho \sigma_1 + (p-p^2) \sigma_2 \rho \sigma_2 + p^2 \sigma_3 \rho \sigma_3,
\label{eq:parab}
\end{eqnarray}
with $p \in [0,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits can be:
\begin{eqnarray}
|\beta(p)\rangle =  (1-p) |0\rangle + \sqrt{p-p^2} |1\rangle +  \sqrt{p-p^2} |2\rangle + p |3\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right) \\
& := |c\rangle + e^{is} |a\rangle + e^{-is} |b\rangle,
\end{align*}
with $\sin s = 2p-1$, so that
this curve fulfills the conditions of  \eref{eq:conditions-vecs}.
This  means that it can be created with the
1PR circuit of figure \fref{FigS2q}. In this
case, matrices $A$ and $B$ can be taken to be:
\begin{align*}
A = \begin{pmatrix}
0 & 1/\sqrt{2} & -i/2 & i/2 \\
-1/\sqrt{2} & 0 & 1/2 & 1/2 \\
1/\sqrt{2} & 0 & 1/2 & 1/2 \\
0 & 1/\sqrt{2} & i/2 & -i/2
\end{pmatrix} \\
B = \begin{pmatrix}
0 & 1 &0 &0 \\
1/\sqrt{2} & 0 & 0 &-1/\sqrt{2} \\
1/2 & 0 & 1/\sqrt{2} & 1/2 \\
1/2 & 0 & - 1/\sqrt{2} & 1/2
\end{pmatrix},
\end{align*}
where again, the first column of $A$ and the last three of $B$ can be chosen arbitrarily. 
As before, we ran this circuit for $25$ values of $p$ between $0$ and $1$, with $20$ repetitions for each,
obtaining as a result the fidelities shown in \fref{FigS2q}.

\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
\end{align*}
with $\sin s= \sqrt{p}$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
Matrices $A$ and $B$ can be obtained as for the other
dynamical maps and the we ran the resulting circuit in ibmq-lima with the same
specifications as for the other examples
and the results are shown in \fref{FigS2q}.
%Note that in this case we actually only need one ancilla qubit
%since the state $|\beta(p)\rangle$ is only two dimensional.

@@

{\color{green}
\begin{figure} % {{{
\centering
\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
\caption{
{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
The implementation was done on IBM's ibmq-lima quantum computer.
We can see that just as in \fref{Fig3}, fidelities are high for points close to the depolarizing channel 
($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
doesn't considerably affect fidelity.}
\label{fid} 
\end{figure} % }}}
}

>>>>

In this section we propose a quantum circuit that simulates $N$-qubit Pauli
channels. \revnote{At this point I am missing a proper definition of a "quantum circuit" consistent with the mathematical formalism. The authors start from the very basic regarding Pauli channels, but give for granted the quantum circuit formalism.} \tbnote{Agregué algo abajo}

@@

Our systems always consists of some number of qubits,
that can be divided into the ones to which we will apply the quantum channel,
 or ``principal qubits'' and the ones that help us complete said operation, or ``ancilla qubits''.
The circuit implements a unitary operator $U$ on the 
system consisting of all the qubits 
and then the principal qubits are measured.
}

 Moreover, we implement the circuit for $N=1$ on a quantum computer
and analyze the results using the diamond norm.
We find that close to the depolarizing channel, the general circuit simulator 
can implement such channels with the highest fidelity.  \\

@@

Finally, using the representation of Pauli channels in a tetrahedron as in
\eref{eq: conditions-tetrahedron}, we show in \fref{Fig3} the diamond
fidelity defined by \eref{eq:diamond-fid} for the channels analyzed.  We can
see that channels close to the completely depolarizing channel (that is close
to the center of the tetrahedron) have a high $f$, while those close to unitary
channels have much lower $f$. \revnote{So another way to see this is that the simulation through the proposed decomposition works only for depolarising channels, and fails otherwise. } 
\tbnote{La respuesta a esto puede incluir lo siguiente: 
It works better for depolarizing channels, yes, but still has considerably big zone with high fidelity.}
 This is reasonable because quantum computers are
prone to errors that depolarize qubits, which isn't very problematic when
trying to simulate depolarization but it is when simulating unitary processes.
Moreover, the algorithm of \fref{Fig2} is not optimal for
unitary channels \revnote{why?} (that is, the channels corresponding to the vertices of the
tetrahedron).  These straightforward channels could be accomplished more
efficiently by simply applying the corresponding Pauli operation directly. \revnote{I wholeheartedly agree with this statement, and I would go so far as to claim that this is true in general, even at the center of the tethraedron.}
\tbnote{Este comentario se conecta con lo del 
primer comentario, que no sé bien cómo contestar.}
Nevertheless, due to its general design to accommodate any Pauli channel, the
algorithm employs numerous quantum gates even in such scenarios. \revnote{but this is a severe disadvantage, that begs the question: what is the advantage?}
\tbnote{As I see it, an advantage is that only one circuit arrengment is needed for any channel. We don't have to change
the circuit to implement different channels, only need to change parameters.
This allows us to consider parametrized circuits and then explore what happens when
we constrain to only one parametrized operation.}\\
\tbnote{Se podría entonces cambiar la ultima oración del texto por la siguiente para que quede más claro:}
{\color{green} This disadvantage comes from the fact
that the circuit is  fully general and applicable to any Pauli channel, but that means that sometimes
it is not the most straightforward algorithm to simulate a Pauli channel.
However, the main advantage is that if we want 
to simulate many Pauli channels (for example,
for simulating a Pauli dynamical map as we will see later),
we only have to change a couple of angles in the circuit and
not completely reconstruct it. 
And as we will see, sometimes only changing
one angle in the circuit will be enough.}

{\color{green}
\subsection{Simulation of a two-qubit Pauli channel}
\tbnote{Voy a agregar toda esta sección sobre el circuito para dos qubits}

For the case of a two-qubit Pauli channel,
the circuit of \fref{Fig1} would have two principal
qubits and four ancilla qubits, on which it would be necessary to create the state $\sum_{\vec{\gamma}} b_{\vec{\gamma}} |\vec{\gamma}\rangle$.
However, the number of ancilla qubits can be reduced for Pauli 
channels in which not all two-qubit Pauli matrices are applied to
the system. For example, consider the following two-qubit dephasing channel:
\begin{align}
\varepsilon (\rho) = (1-p) \rho + \dfrac{p}{3} (I \otimes \sigma_z) \rho (I \otimes \sigma_z) +  \dfrac{p}{3}(\sigma_z \otimes I) \rho (\sigma_z \otimes I) +  \dfrac{p}{3}(\sigma_z \otimes \sigma_z) \rho (\sigma_z \otimes \sigma_z),
\label{2qbit-c}
\end{align}
where $p \in [0,1]$ is a parameter that defines the channel. 
Since this channel has $4$ Pauli operations, 
only $2$ ancilla qubits will be necessary, and it can be implemented
using the circuit of \fref{2qbit}a).

@@

Just as for the one-qubit Pauli channels, this 
channel was implemented on IBM's ibmq-lima  quantum computer and we obtained the Choi 
matrix by doing quantum process tomography on
the principal qubits. Then, we calculated the diamond fidelity for different values of $p$ and
obtained the results shown in \fref{2qbit}b).

@@

{\color{green} As before, from the definition of a 1PR, we know that $U(p)$ can be decomposed as $ARB$, where 
$A,B$ are unitary operators acting on the $N$-qubit system
and $R$ is a rotation applied to one qubit.
From theorem 1, we conclude that $R$ can be taken in general as a $\sigma_3$
rotation of angle $2s(p)$ applied to the last qubit and controlled by some of the other ones.
Given  this, to prove the result of this theorem,
we will apply $U(p)$ to $|j\rangle$ by first applying $B$,
then $R_{\sigma_3}(2s(p))$ and finally $A$, with
the goal of getting to \eref{eq:uj}. }

@@

Moreover, it is possible to construct a 1PR circuit to generate any given curve of 
states described by \eref{eq:curve-states}. 
One approach to achieve this is by utilizing the circuit 
depicted in \fref{Fig4}, 
with the parametrized rotation $R$ applied to the last qubit controlled by all the 
other qubits. There is some freedom when defining
the operators $A$ and $B$, we only need
to make sure that: \revnote{How can it make sense to define A and B applied respectively to the last 3 and the first qubit?} 
\tbnote{Reescribí la oración anterior para no decir que es una definición,
sino que queda algo de libertad (aunque igual lo decía después de la ecuación)}
\begin{align}
&B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N}-1 \rangle + \sqrt{\langle b | b \rangle} |2^{N}-2\rangle + \sqrt{\langle c |c \rangle} |2^N-3\rangle, \nonumber \\
&A|2^N-1 \rangle = \frac{1}{\sqrt{\langle a | a \rangle}} |a\rangle,\; A|2^{N}-2\rangle = \frac{1}{\sqrt{\langle b | b \rangle}}|b\rangle, \; A|2^{N}-3\rangle = \frac{1}{\sqrt{\langle c | c \rangle}}|c\rangle.
\label{eq:BA}
\end{align}
\revnote{Please, at least give an example of this semiarbitrary construction of A and B.}
\tbnote{Hay ejemplos en los ejemplos de abajo.}
The remaining part of the operators $A$ and $B$ can be defined
in any arbitrary manner as long as they are unitary. 
Then, by following the calculations of applying 
$A R_{\sigma_3}(2s(p)) B$ to $|0\rangle$,
it can be shown that the curve of states created is that described in \eref{eq:curve-states}.
\revnote{I don't understand what operatively is happening here. Select the state 0, apply B, apply s, apply A and then "straight forward calculations" lead to what?}
\tbnote{Reescrib\'i la oraci\'on anterior de forma que creo que se entiende mejor.}

To see that $A R_{\sigma_3}(s(p)) B |0\rangle$ in fact creates
the curve of states described in \eref{eq:curve-states}, \revnote{to see what?} \tbnote{Ya cambié la oración anterior, pero siento que queda redundante. Creo que como estaba antes ``to see it'', era suficiente.} we can rewrite the expression of $B|0\rangle$ by 
separating the first $N-1$ qubits from the last one:
$$B|0\rangle = \sqrt{\langle a | a \rangle} |2^{N-1}-1\rangle |1\rangle + \sqrt{\langle b | b \rangle} |2^{N-1}-1\rangle |0\rangle + \sqrt{\langle c | c \rangle} |2^{N-1}-2\rangle |1\rangle.$$
Since the parametrized rotation $R_{\sigma_3}(2s(p))$ is controlled by all the first $N-1$ qubits, it only applies to the first two terms of $B|0\rangle$. As a result, we obtain: \revnote{so this is just the proof that the proposed operative definition of A and B is properly normalised, right?} \tbnote{No entiendo la pregunta, pero creo que la respuesta es no}

@@

\begin{itemize}
\item \textbf{Depolarizing:} This dynamical map is given by
\begin{align*}
\varepsilon_p(\rho) = (1-3p/4) \rho + (p/4) \sigma_1 \rho \sigma_1 + (p/4) \sigma_2 \rho \sigma_2 + (p/4) \sigma_3 \rho \sigma_3,
\end{align*}
with $p \in [0,1]$. 
Therefore, the curve of states $|\beta(p)\rangle$ needed on the ancilla
qubits is such that ${|\beta_0(p)|}^2= (1-3p/4)$, ${|\beta_1(p)|}^2 =
{|\beta_2(p)|}^2 = {|\beta_3(p)|}^2 = p/4$.  Then, taking the $\beta_j$ to be
real, the curve of states can be 
\begin{align*}
|\beta(p) \rangle = \sqrt{1-3p/4} |0\rangle + \sqrt{p/4} |1\rangle + \sqrt{p/4} |2 \rangle  + \sqrt{p/4} |3\rangle.
\end{align*}
This state can be rewritten as:
\begin{align*}
|\beta(p)\rangle =& \; e^{is} \left( \dfrac{1}{2} |0\rangle - \dfrac{i}{2\sqrt{3}} |1\rangle 
      - \dfrac{i}{2\sqrt{3}} |2 \rangle - \dfrac{i}{2\sqrt{3}} |3\rangle \right) \\
& + e^{-is} \left( \dfrac{1}{2} |0\rangle + \dfrac{i}{2\sqrt{3}} |1\rangle 
      + \dfrac{i}{2\sqrt{3}} |2\rangle + \dfrac{i}{2\sqrt{3}} |3 \rangle \right) \\
\equiv &\; e^{is} |a\rangle + e^{-is} |b\rangle
\end{align*}
\revnote{to be consistent with the previous formalism, the states should be 0,1,2,3} \tbnote{Done.}
with $\sin s = \sqrt{3p/4}$.
We can see that this curve satisfies the conditions of \eref{eq:conditions-vecs}, meaning that it can be created with a 
1PR circuit.
Explicitly, following the discussion after theorem \ref{theorem2},
we know that this curve of states can be constructed by 
the circuit of \fref{FigS2q}.

@@

The circuit requires defining $A$ and $B$ as in  \eref{eq:BA}, and for the particular
vectors $|a\rangle, |b\rangle, |c \rangle$ of this dynamical map, we have that
\begin{align*}
A = \begin{pmatrix}
0 & 0 & 1/\sqrt{2} & 1/\sqrt{2} \\
1/\sqrt{6} & -1/\sqrt{2} & i /\sqrt{6} & -i /\sqrt{6} \\
1/\sqrt{6}  & 1/\sqrt{2} & i/\sqrt{6} & -i/\sqrt{6} \\
-\sqrt{2/3} & 0 & i/\sqrt{6} & -i/\sqrt{6}
\end{pmatrix} , \; B = \begin{pmatrix}
0 & 0 & 0& 1 \\
0 & 0 & 1 & 0 \\
1/\sqrt{2} & -1/\sqrt{2} & 0 & 0 \\
1/\sqrt{2} & 1/\sqrt{2} & 0 & 0 
\end{pmatrix},
\end{align*}
where, as mentioned before, the first column of $A$ and the
last three of $B$ can be chosen arbitrarily as long as the resultant matrices are unitary. 
We ran this circuit in IBM's quantum computer ibmq-lima for $25$ different values of $p$ between $0$ and $1$,
with $20$ repetitions for each value of $p$.
The diamond fidelity was calculated in each case and is shown in \fref{fid}.

\item \textbf{Parabolic dynamical map:} We define the parabolic dynamical map as:
\begin{eqnarray}
\epsilon(\rho) =  {(1-p)}^2  \rho + (p-p^2) \sigma_1 \rho \sigma_1 + (p-p^2) \sigma_2 \rho \sigma_2 + p^2 \sigma_3 \rho \sigma_3,
\label{eq:parab}
\end{eqnarray}
with $p \in [0,1]$. 
If we take the $\beta_j$ to be real,
the curve of states needed on the ancilla qubits can be:
\begin{eqnarray}
|\beta(p)\rangle =  (1-p) |0\rangle + \sqrt{p-p^2} |1\rangle +  \sqrt{p-p^2} |2\rangle + p |3\rangle.
\end{eqnarray}
This can be rewritten as
\begin{align*}
|\beta(p)\rangle =&\; \left( \dfrac{1}{2}|0\rangle + \dfrac{1}{2} |3\rangle \right) + e^{is} \left( \dfrac{i}{4}|0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle - \dfrac{i}{4} |3\rangle \right) \\
& + e^{-is}  \left( \dfrac{-i}{4} |0\rangle + \dfrac{1}{4} |1\rangle + \dfrac{1}{4} |2\rangle + \dfrac{i}{4} |3\rangle \right) \\
\equiv & \; |c\rangle + e^{is} |a\rangle + e^{-is} |b\rangle,
\end{align*}
with $\sin s = 2p-1$, so that
this curve fulfills the conditions of  \eref{eq:conditions-vecs}.
This  means that it can be created with the
1PR circuit of figure \fref{FigS2q}. In this
case, matrices $A$ and $B$ can be taken to be:
\begin{align*}
A = \begin{pmatrix}
0 & 1/\sqrt{2} & -i/2 & i/2 \\
-1/\sqrt{2} & 0 & 1/2 & 1/2 \\
1/\sqrt{2} & 0 & 1/2 & 1/2 \\
0 & 1/\sqrt{2} & i/2 & -i/2
\end{pmatrix},
B = \begin{pmatrix}
0 & 1 &0 &0 \\
1/\sqrt{2} & 0 & 0 &-1/\sqrt{2} \\
1/2 & 0 & 1/\sqrt{2} & 1/2 \\
1/2 & 0 & - 1/\sqrt{2} & 1/2
\end{pmatrix},
\end{align*}
where again, the first column of $A$ and the last three of $B$ can be chosen arbitrarily. 
As before, we ran this circuit for $25$ values of $p$ between $0$ and $1$, with $20$ repetitions for each,
obtaining as a result the fidelities shown in \fref{fid}.

\item \textbf{Bit flip map:} 
This dynamical map is defined as
\begin{align*}
\varepsilon_p(\rho) = (1-p)\rho + p\sigma_1 \rho \sigma_1,
\end{align*}
for $p \in [0,1]$. 
In particular, if we take the $\beta_j$ to be real,
we need to create the curve of states:
\begin{align*}
|\beta(p)\rangle = \sqrt{1-p} |0\rangle +\sqrt{p} |1\rangle.
\end{align*}
This can be rewritten as
\begin{align*}
|\beta(p) \rangle = e^{is}  \left(\frac{1}{2} |0\rangle - \dfrac{i}{2} |1\rangle \right) + e^{-is} \left( \frac{1}{2} |0\rangle + \frac{i}{2} |1\rangle \right),
\end{align*}
with $\sin s= \sqrt{p}$.
Therefore, we can see that the curve satisfies the conditions of  \eref{eq:conditions-vecs} 
and it can be created with a 1PR circuit.
Matrices $A$ and $B$ can be obtained as for the other
dynamical maps and we ran the resulting circuit in ibmq-lima with the same
specifications as for the other examples,
with the results are shown in \fref{fid}.
%Note that in this case we actually only need one ancilla qubit
%since the state $|\beta(p)\rangle$ is only two dimensional.

@@

{\color{green}
\begin{figure} % {{{
\centering
\includegraphics[width=0.60\textwidth]{images/dynamic-fidelitites.png}
\caption{
{\bf Fidelitis for dynamical maps.} Results of the fidelities obtained when simulating the three dynamical maps considered (depolarizing, parabolic and bit flip). 
The implementation was done on IBM's ibmq-lima quantum computer.
Furthermore, we can see that the fidelities are comparable to those of \fref{Fig3}, so that using the 1PR circuit
doesn't considerably affect fidelity.}
\label{fid} 
\end{figure} % }}}
}

From the results of \fref{fid}, we can see that just as in figure 
\fref{Fig3}, fidelities are high for points close to the depolarizing channel 
($p=1$ for depolarizing map, $p=1/2$ for parabolic map) and lower for points close
to unitary channels ($p=0$ for all maps and $p=1$ for parabolic and bit flip).
Furthermore, we can see that the actual values of the fidelities are comparable
to those of \fref{Fig3}, which means that
using the 1PR circuit as opposed to 
implementing each channel with \fref{Fig2}
does not considerably affect fidelity.
